% foreword
\begin{myparagraph}
    Now that we introduced rooted-microbundles,
    we are able to define the wedge sum.
    As we will see in the subsequent proof,
    the definition of the wedge sum
    it is necessary to have a fixed rooting given because otherwise
    one would have to choose a rooting which the resuling microbundle depends on,
    hence not being well-defined.

    Given a quotient space $A \sqcup B / \sim$ and maps $f: A \to C$ and $g: B \to C$, we define
    \[ f \cup g: (A \sqcup B / \sim) \to C \twith \]
    \[ x \mapsto \begin{cases} f(x) & \text{if } x \in A \\ g(x) &\text{if } x \in B \end{cases}.\]
    Clearly, this map is only well-defined if $a \sim b \implies f(a) = g(b)$.
\end{myparagraph}

% definition
\begin{mystatement}{definition}{suspension::wedge}[70] % ? remove citation
    Let $\ba$ and $\bb$ be two rooted microbundles over $A$ and $B$.
    % microbundle
    The \defterm{wedge sum} $\ba \vee \bb$ of $\ba$ and $\bb$ is a microbundle
    \[ A \vee B \xto{i_a \cup i_b} E(\ba \vee \bb) \xto{j_a \cup j_b} A \vee B \]
    with the total space defined as
    \[ (E(\ba) \sqcup E(\bb)) / f(e_a) \sim e_a \]
    where $f: W_a \isomto W_b$ is a representative for $\inv{R_b} \circ R_a$.
    
    % rooting
    We equip $\ba \vee \bb$ with a rooting
    \[ \germdef{R}{E((\ba \vee \bb)\restr{a_0})}{\be{a_0}} \]
    represented by any representative for $R_a$ (or $R_b$).
\end{mystatement}

% proof
\begin{myproof}[that $\ba \vee \bb$ is a rooted microbundle]
    Let $f: W_a \isomto W_b$ be a representative for $\inv{R_b} \circ R_a$.

    % rooted microbundle
    \begin{sectionize}
        \item $\ba \vee \bb$ is a rooted microbundle
        \begin{itemize}
            % injection
            \item The injection map $i_a \cup i_b$ is well-defined because 
            \[ [i(a_0)] = [i_a(a_0)] = [f(i_a(a_0))] = [i_b(b_0)] = [i(b_0)] \]
            and continuous since both $i_a$ and $i_b$ are continuous.
            % projection
            \item The projection map $j_a \cup j_b$ is well-defined because
            \[ \forall e \in W_a: [j(e)] = [j_a(e)] = [a_0] = [b_0] = [j_b(f(e))] = [j(f(e))] \]
            and continuous since both $j_a$ and $j_b$ are continuous.
            % compatibility
            \item The composition $j \circ i$ is the identity because
            \[ \forall a \in A: j(i(a)) = j(i_a(a)) = j_a(i_a(a)) = a \]
            since $j_a \circ i_a = id_A$ (symmetrical for $B$).
        \end{itemize}
        % local triviality
        It remains to be shown that $\ba \vee \bb$ is locally trivial.

        Let $x \in A \vee B$.
        For reasons of symmetry, we can assume that $x \in A$.
        \begin{caselist}
            % trivial case
            \item $x \neq a_0$
            
            % construct
            Choose a local trivialization $(U, V, \phi)$ for $x$ in $\ba$.
            Without loss of generality,
            we can assume that $U \cap B = \emptyset$ by subtracting
            $\{a_0\}$ from $U$ if necessary.
            Note that $\{a_0\}$ is closed since $A$ is hausdorff.
            
            % show
            Now we can simply use this trivialization for $\ba \vee \bb$, because
            $U \sub A$ is open in $A \vee B$ and
            $V \sub E(\ba)$ is open in $E(\ba \vee \bb)$.
            Furthermore, since $i$ and $j$ reduce to $i_a$ and $j_a$,
            it follows that $\phi$ commutes with $i$ and $id \cross 0$
            as well as with $j$ and $\pi_1$.

            % special case
            \item $x = a_0$
            
            Let $(U_a, V_a, \phi_a)$ and $(U_b, V_b, \phi_b)$ be local trivializations
            for $a_0 = b_0$ in $\ba$ and $\bb$.

            % open
            Since $W_a \sub E(\bab)$ is open,
            there exists an open subset
            $W_a' \sub E(\ba)$ such that $W_a = W_a' \cap E(\bab)$.

            Let $U_a' \sub A$ be an open neighborhood of $a_0$ and $\eps > 0$ such that
            \[ V_a' := U_a' \cross \ball[\eps] \sub \phi_a(W_a'). \]
            This allows us to define the map
            \[ \phi_a': V_a' \isomto \phi_a'(V_a') \sub A \cross \R^n \twith \]
            \[ \phi_a'(e) = (j_a(e), (\snd{\phi_b} \circ f \circ \inv{\phi_a})(a_0, \snd{\phi_a}(e))). \]

            Now we can show local triviality in $a_0$ using the homeomorphism
            \[ \phi_a' \cup \phi_b: V_a' \cup V_b \isomto \phi_a'(V_a' \cup V_b) \sub (A \vee B) \cross \R^n \]

            This map is well-defined, because
            \[ \phi_a'(e) = (a_0, (\snd{\phi_b} \circ f \circ \inv{\phi_a})(a_0, \snd{\phi_a}(e))) \]
            \[ = (b_0, \snd{\phi_b}(f(e))) = (j_b(f(e)), \snd{\phi_b}(f(e))) = \phi_b(f(e)). \]

            Homeomorphy follows from the fact
            that both $\phi_a'$ and $\phi_b$ are homeomorphisms,
            and that $\phi_a'(e_a) = \phi(e_b) \implies f(e_a) = e_b$. 

            Commutativity between $i_a \cup i_b$ and $id \cross 0$
            as well as between $j_a \cup j_b$ and $\pi_1$
            is inherited from $\phi_a$ and $\phi_b$.
            Note that $\phi_a(i_a(a)) = (a, 0) = \phi_a'(i_a(a))$.

            Applying \myintref{microbundle::local} yields that $\ba \vee \bb$ is locally trivial.
        \end{caselist}
        
        % well-defined
        \item $\ba \vee \bb$ is well-defined

        Let $f'$ be another representative for $\inv{R_b} \circ R_a$ and $(\ba \vee \bb)'$ the resulting wedge sum.
        We need to find an isomorphism-germ that extends $\inv{R'} \circ R$.
        
        In order to do this,
        choose an open neighborhood $V \sub E(\ba\restr{a_0})$
        of $i_a(a)$ where $f$ and $f'$ agree.
        
        By subtracting the closed set $\inv{j_a}(a_0) - V$
        from $E(\ba \vee \bb)$ and $E(\ba \vee \bb)'$,
        the microbundles remain unchanged due to \myintref{microbundle::total}.
        
        But now the total spaces $E(\ba \vee \bb)$ and $E((\ba \vee \bb)')$ are the same.
        That is because $E(\ba \vee \bb)$ and $E((\ba \vee \bb)')$
        could only differ in $\inv{j_a}(a_0) - V$.

        
        Furthermore, since injection and projection are defined exactly the same,
        it follows that the identity $\germ{(\ba \vee \bb)}{(\ba \vee \bb)'}$
        is an isomorphism-germ.
        Together with
        \[ \inv{R'} \circ R = \inv{R} \circ R = I, \]
        which completes the proof.
    \end{sectionize}
\end{myproof}