% hausdorff
\begin{myparagraph}
    The following definition requires the base spaces to be hausdorff.
    This is useful because this implies that the singleton containing only the base point is closed,
    and can therefore be removed from any open set without losing openness.  
\end{myparagraph}

% definition
\begin{mydefinition}{suspension::wedge}
    Let $\ba$ and $\bb$ be two rooted microbundles over $A$ and $B$.
    % microbundle
    The \defterm{wedge sum} $\ba \vee \bb$ of $\ba$ and $\bb$ is a rooted microbundle over $A \vee B$
    \[ A \vee B \xto{i_a \vee i_b} E(\ba \vee \bb) \xto{j_a \vee j_b} A \vee B \]
    with the total space $E(\ba \vee \bb)$ being defined as
    \[ (E(\ba) \sqcup E(\bb)) / f(e_a) \sim e_a \]
    where $f: W_a \isomto W_b$ is a representative for $\inv{R_b} \circ R_a$.
    
    % rooting
    We equip $\ba \vee \bb$ with a rooting
    \[ \germdef{R}{E((\ba \vee \bb)\restr{a_0})}{\be{a_0}} \]
    represented by any representative for $R_a$ (or $R_b$).
\end{mydefinition}

% proof
\begin{myproof}[that $\ba \vee \bb$ is a rooted microbundle]
    Let $f: W_a \isomto W_b$ be a representative for $\inv{R_b} \circ R_a$.
    \begin{enumerate}
        % rooted microbundle
        \item $\ba \vee \bb$ is a rooted microbundle:
        \begin{itemize}
            % injection
            \item The injection map $i_a \vee i_b$ is well-defined because 
            \[ i(a_0) = i_a(a_0) = f(i_a(a_0)) = i_b(b_0) = i(b_0) \]
            and continuous since both $i_a$ and $i_b$ are continuous.
            % projection
            \item The projection map $j_a \vee j_b$ is well-defined because
            \[ \forall e \in W_a: j(e) = j_a(e) = a_0 = b_0 = j_b(f(e)) = j(f(e)) \]
            and continuous since both $j_a$ and $j_b$ are continuous.
            % compatibility
            \item The composition $j \circ i$ equals $id_{A \vee B}$ because
            \[ \forall a \in A: j(i(a)) = j(i_a(a)) = j_a(i_a(a)) = a \]
            since $j_a \circ i_a = id_A$ (analogous for $B$).
        \end{itemize}
        % local triviality
        It remains to be shown that $\ba \vee \bb$ is locally trivial.

        Let $x \in A \vee B$.
        For symmetry reasons, we may assume $x \in A$.
        Consider the two cases:
        \begin{enumerate}
            % trivial case
            \item $x \neq a_0$:
            
            Choose a local trivialization $(U, V, \phi)$ for $x$ in $\ba$.
            We can assume $U \cap B = \emptyset$ by subtracting $U$ by $\{a_0\}$ which is closed since $A$ is hausdorff.
            
            Now we can simply take this trivialization for $\ba \vee \bb$
            since $U$ is open in $A \vee B$, $V$ is open in $E(\ba \vee \bb)$ and $V \cong U \times \R^n$.
            % special case
            \item $x = a_0$:
            
            % construct (U_a, V_a, phi_a)
            The subspace topology of $E(\ba\restr{a_0})$ yields an open subset
            $W_a' \sub E(\ba)$ such that $W_a = W_a' \cap E(\ba\restr{a_0})$.
    
            Let $(U_a, V_a, \phi_a)$ be a local trivialization of $a_0$ in $\ba$
            where we restricted $E(\ba)$ to 
            \[ (E(\ba) - \inv{j_a}(a_0)) \cup W_a'. \]
            The resulting total space is an open neighborhood of $i_a(A)$ since $\inv{j_a}(a_0)$
            is closed ($A$ is hausdorff) and $W_a'$ is open containing $i_a(a_0)$.
            The fact that $\ba$ is still a microbundle is justified by \intref{microbundle::total}.
            It follows that
            \[ V_a \cap E(\bab) \sub W_a. \]

            % construct (U_b, V_b, phi_b)
            The subspace topology of $E(\bbb)$ yields an open subset
            $W_b' \sub E(\bb)$ such that $f(V_a \cap E(\bab)) = W_b' \cap E(\bbb)$

            Similarly, let $(U_b, V_b, \phi_b)$ be a local trivialization of $b_0$ in $\bb$
            where we restricted $E(\bb)$ to
            \[ (E(\bb) - \inv{j_b}(b_0)) \cup W_b'. \]
            It follows that
            \[ f(V_b \cap E(\bbb)) \sub f(V_a \cap E(\bab)). \]

            It follows by construction that
            \[ V_b \cap E(\bbb) \sub W_b \tand V_a \cap E(\bab) \sub W_b \cap E(\bbb). \]

            We denote $X$ to be an open subset of $\R^n$ with
            \[ X = (\snd{\phi_a} \circ \inv{f})(V_b \cap E(\bbb)). \]

            By definining 
            \[ V_a' = \inv{\phi_a}(U_a \times X) \]
            together with
            \[ \phi_a': V_a' \isomto U_a \times \R^n \]
            \[ e \mapsto (j_a(e), (\snd{\phi_b} \circ f \circ \inv{\phi_a})(a_0, \snd{\phi_a}(e))) \]
            we finally have a local trivialization $(U_a \vee U_b, (V_a' \sqcup V_b) / \sim, \phi_a' \vee \phi_b)$ of $a_0$ in $\ba \vee \bb$.

            The homeomorphism is well-defined because for every $e \in V_b \cap E(\bbb)$
            \[ \phi_a'(\inv{f}(e)) = (a_0, (\snd{\phi_b} \circ f \circ \inv{\phi_a})(a_0, \snd{\phi_a}(e))) \]
            \[ = (a_0, \snd{\phi_b}(f(\inv{f}(e)))) = (a_0, \snd{\phi_b})(e) \]
            \[ = (b_0, \snd{\phi_b}(e)) = \phi_b(e). \]
            
            Compatibility with injection and projection maps follows is inherited
            from the summands $\ba$ and $\bb$.
        \end{enumerate}
        % well-defined
        \item The wedge sum $\ba \vee \bb$ is independant of the choice of $f$ up to rooted-isomorphy:

        Let $f'$ be another representative for $\inv{R_b} \circ R_a$ and $(\ba \vee \bb)'$ the resulting wedge sum.
        
        We need to find an isomorphism-germ that extends
        \[ \inv{R'} \circ R = \inv{R} \circ R = id. \]
        Choose an open neighborhood $V \sub E(\ba\restr{a_0})$ of $i_a(a)$ where $f$ and $f'$ agree.
        
        By subtracting $\inv{j_a}(a_0) - V$ from $E(\ba \vee \bb)$ and $E(\ba \vee \bb)'$
        the microbundles remain unchanged using \intref{microbundle::total}.
        
        So the resulting total spaces $E(\ba \vee \bb)$ and $E(\ba \vee \bb)'$ agree
        as well as the injection and projection maps that are defined in the same way.
        
        Using the modified total spaces,
        it follows that the identity $\germ{(\ba \vee \bb)}{(\ba \vee \bb)'}$
        is an isomorphism-germ.
        Together with $\inv{R'} \circ R = id$, this completes the proof.
    \end{enumerate}
\end{myproof}