% foreword
\begin{myparagraph}
    We are primarily interested in microbundles over topological manifolds.
    In this case, as topological manifolds are paracompact and hausdorff,
    triviality has stronger implications for the total space.
\end{myparagraph}

% lemma
\begin{mystatement}{lemma}{microbundle::paracompact}[57]
    A microbundle $\bb$ over a paracompact hausdorff space $B$ is trivial
    if and only if there exists an open neighborhood $V$ of $i(B)$ such that $V \cong B \cross \R^n$
    with injection and projection maps being compatible with this homeomorphism.
\end{mystatement}

% afterword
\begin{myparagraph}
    This means that there exists an open subset of $E(\bb)$ being homeomorphic to the entire $B \cross \R^n$,
    instead of only a neighborhood of $\cyldown{B}$ given by the definition of triviality.
\end{myparagraph}

% proof
\begin{myproof}
    We show both implications.

    `$\implies$'

    By restricting $E(\bb)$ to an open neighborhood
    and applying \myintref{microbundle::total} if necessary,
    we may assume that the entire $E(\bb)$ is an open subset of $B \cross \R^n$.

    Hence,
    there exist $B_i \sub B$ open and $0 < \eps_i < 1$ with $\bigcup_{i \in I} B_i = B$ such that
    \[ \bigcup_{i \in I } B_i \cross \ball[\eps_i] \sub E(\bb). \]
    Without loss of generality,
    we may assume that the collection $\{B_i\}$ is locally finite by refining this collection if necessary,
    utilizing the fact that $B$ is paracompact.

    Furthermore, $B$ being paracompact hausdorff yields a partition of unity
    \[ f_i: B \to [0, 1] \twith \supp{f_i} \sub B_i\]
    such that $\sum_{i \in J}f_i = 1$.
    
    We define a map $\lambda: B \to (0, \infty)$ with $\lambda = \sum_{i \in J} \eps_i f_i$,
    which has the property that $\abs{x} < \lambda(b) \implies (b, x) \in E(\bb)$ because
    \[ \abs{x} < \lambda(b) \]
    \[ \iff  \abs{x} < \eps_{i_1} f_{i_1}(b) + \cdots + \eps_{i_n} f_{i_n}(b) \]
    \[ \iff 0 < (\eps_{i_1} - \abs{x}) f_{i_1}(b) + \cdots + (\eps_{i_n} - \abs{x}) f_{i_n}(b) \]
    \[ \implies \exists i \in J: 0 < (\eps_{i} - \abs{x}) f_{i}(b) \]
    \[ \implies (b, x) \in B_i \cross \ball[\eps_i]  \implies (b, x) \in E(\bb). \]

    Finally, we have a homeomorphism between the open subset
    $\set{(b, x) \in B \cross \R^n}{\abs{x} < \lambda(b)} \sub E(\bb)$ and $B \cross \R^n$ via
    \[ (b, x) \mapsto (b, \frac{x}{\lambda(b) - \abs{x}}). \]
    Since $(b, 0)$ is mapped to $(b, 0)$, it follows that
    the homeomorphism commutes with the injection and projection maps.
    % TODO: explain commutativity

    `$\impliedby$'

    This is simply a weakening of the definition of triviality.
\end{myproof}